\LARGE \bf Cross Validation of Emotional Features with a non-Anthropomorphic Platform

### 2017-01-26 RO-MAN-2017-1/RO-MAN2017.tex
Update RO-MAN2017.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Robots should be able to express emotional states to interact with people as social agents. Emotions are a peculiar characterization of humans and usually conveyed through face expression, body language and voice. However there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks, which require a specific structure. This is the case of home cleaners, package carriers, and many others platforms. Therefore, emotional states need to be represented by exploiting other features, such as movements and shape changes. This paper presents a case study, which studies emotion expression in non-anthropomorphic platform and how it is perceived by humans. This case study was design base on results obtained from a previous experiment, which was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness. Results of the case study  show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions. Additionally, it was done a small scene to verify if people prefer emotions with or without emotion. 
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Robots should be able to express emotional states to interact with people as social agents. Emotions are a peculiar characterization of humans and usually conveyed through face expression, body language and voice. However, there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks that require a specific structure. This is the case of home cleaners, package carriers, and many others platforms. Therefore, emotional states need to be represented by exploiting non-anthropomorphic features, such as movements and shape changes. This paper presents a case study concerning emotion expression in non-anthropomorphic platform and how it is perceived by humans. This case study was designed basing on results obtained from a previous experiment, done to assess precise values for linear velocity, angular velocity, oscillation angle, direction, and orientation that could be used to express happiness, anger, fear, and sadness. Results of the case study  show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions. Additionally, a small scene was played to verify whether people prefer actions with or without emotion expression. 
\end{abstract}
